---
title: "NSF Graduate Research Fellowships Program (GFRP) Data Visualization"
output: pdf_document
author: "Natalie Sarabosing"
date: "2023-12-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(maps)
library(usdata)
library(gifski)
library(av)
library(mapproj)
library(gganimate)
library(transformr)
```

### Author's Note: 
This file is the second half of my work from the Fall 2023 Early Undergraduate Research in Statistics course (36-297). My goal with this .Rmd file was to create an animated time-series choropleth map of the cleaned NSF data (see the NSF Data Cleaning file). I wasn't quite able to successfully accomplish the animation by the end of the semester, but did manage to create the choropleth maps for Baccalaureate Institutions. The following file is less polished, and is essentially my exploration and debugging process. I would enthusiastically invite anyone to use this file as a jumping-off point to animate those Baccalaureate Institution maps, and to adapt the code to visualize the Current Institutions of grant awardees. Much of my code is based off of code from Professor Spencer Koerner's Statistical Graphics & Visualization course (36-315). 


```{r}
# Reading in the cleaned NSF dataset
nsf_done <- read.csv("nsf_fully_cleaned_12-1.csv")

# Reading in data for the choropleth map boundaries
us_data <- map_data("state")
county_data <- map_data("county")
```


```{r}
# Graphing state boundaries
state_borders <- map_data("state") 
head(state_borders)
state_borders %>%
ggplot() + 
    geom_polygon(aes(x = long, y = lat, group = group), color = "black") 
```

```{r}
# Processing the NSF data to match the state data formats (i.e. abbreviated)
nsf_done$BI_State_Full <- abbr2state(nsf_done$BI_State)
nsf_done$BI_State_Full <- tolower(nsf_done$BI_State_Full)
head(nsf_done)
```

```{r}
# Processing state data
state_names <- rownames(state.x77)
state_data <- as_tibble(state.x77)
state_data <- state_data %>%
  mutate(state = state_names) %>%
  mutate(state = tolower(state))

# Making a copy of the state column 
nsf_done$state <- nsf_done$BI_State_Full
head(nsf_done$state)
```

```{r}
# Preprocessing the NSF data again to try and reoganize by year for animation
nsf2023 <- subset(nsf_done, Year == 2023, select = c(Year, state))
df2023 <- as.data.frame(table(nsf2023$state))
df2023$state <- df2023$Var1

# Making a dataset based on the NSF frequency data of how many grant awardees came from institutions in any given state
df_states = data.frame(matrix(NA, nrow = 1, ncol = 3))
df_states <- df_states %>% 
        rename("year" = "X1",
               "state" = "X2",
               "freq" = "X3") 
                  # This is the number of awardees that came from a school in that state in that year

nsftemp <- subset(nsf_done, Year != 6, select = c(Year, state))
  
for(i in 0:53) { 
   nsftemp <- subset(nsf_done, Year == 2023-i,å select = c(Year, state))
   df_temp <- as.data.frame(table(nsftemp$state))
   df_temp <- df_temp %>%
        rename("state" = "Var1",
               "freq" = "Freq")
   df_temp$year <- 2023-i
   df_states <- bind_rows(df_states, df_temp)
}
df_states <- df_states[-1,]
head(df_states)
```

```{r}
# Creating a copy of the previous frequency dataset to work with
state_plot_data2 <- df_states

# Attempting to format the year as a date
state_plot_data2 <- df_states %>%
  mutate(year = as.Date(year, format = "%Y"))
```

```{r}
# Join state_data data to state_borders
state_plot_data <- state_borders %>%
  left_join(df_states, #<<
            by = c("region" = "state"))
```


```{r}
# Attempt 1 at making a choropleth map
state_plot_data %>%
ggplot() + 
    geom_polygon(aes(x = long, y = lat, group = group, fill = freq), color = "black") + 
    scale_fill_gradient2(low = "#d9f0a3", mid = "#78c679", 
                         high = "#00441b", midpoint = median) +
    theme_void() +
    coord_map("polyconic") + 
    labs(
      title = "NSF GFRP Awardees by State",
      subtitle = 2023-i,
      caption = "National Science Foundation",
      fill = "Frequency"
    ) +
    theme(legend.position = "bottom")
```



```{r, message = FALSE, warning = FALSE}
# Trying to use gganimate to create the choropleth maps

myPlot <- ggplot(state_plot_data) + 
  geom_polygon(aes(x = long, y = lat, group = group, fill = freq), color = "black") + 
  scale_fill_gradient2(low = "#d9f0a3", mid = "#78c679", 
                       high = "#00441b", midpoint = 30) +
  theme_void() +
  coord_map("polyconic") + 
  transition_states(year,
                    transition_length = 0.5,
                    state_length = 1) +
  labs(
    title = "NSF GFRP Awardees by State",
    subtitle = year,
    caption = "National Science Foundation",
    fill = "Frequency"
  ) +
  theme(legend.position = "bottom")

```

```{r}
animate(myPlot, fps = 10, renderer = gifski_renderer())
anim_save("output2.gif")
```


```{r}
# Giving up on gganimate for now
state_plot_data <- subset(state_plot_data, year >= 1970, select = c(long, lat, group, order, region, year, freq))
```

```{r}
# Attempt 2: Using a for loop (unsuccessful)
plot1 = NA
for(i in 0:0) { # will be to 68
  state_plot_temp <- subset(state_plot_data, year == 2023-i, select = c(long, lat, group, order, region, year, freq))
  
  plot <- ggplot(state_plot_temp) + 
    geom_polygon(aes(x = long, y = lat, group = group, fill = freq), color = "black") + 
    scale_fill_gradient2(low = "#d9f0a3", mid = "#78c679", 
                         high = "#00441b", midpoint = median) +
    theme_void() +
    coord_map("polyconic") + 
    labs(
      title = "NSF GFRP Awardees by State",
      subtitle = 2023-i,
      caption = "National Science Foundation",
      fill = "Frequency"
    ) +
    theme(legend.position = "bottom")
  plot1 = plot
}
plot1
```


```{r}
# Attempt 3: Simply generating choropleth maps by year
state_plot <- subset(state_plot_data, year == 2023, select = c(long, lat, group, order, region, year, freq))

ggplot(state_plot) + 
  geom_polygon(aes(x = long, y = lat, group = group, fill = freq), color = "black") + 
  scale_fill_gradient2(low = "#d9f0a3", mid = "#78c679", 
                       high = "#00441b", midpoint = 250) +
  theme_void() +
  coord_map("polyconic") + 
  labs(
    title = "NSF GFRP Awardees by State",
    subtitle = 2023,
    caption = "National Science Foundation",
    fill = "Frequency"
  ) +
  theme(legend.position = "bottom")


# Code for exporting the map as a .png:
# png(file=paste(2023,".png",sep=""), width = 600, height = 400)
# myPlot
```